Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
temp

>>>>

Model-based software diagnosis has been

model-based software debugging, from the DX community, has been shown to be similar to slicing Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many inter- esting techniques having been pursued because of scalability. We have achieved it with a type of program slicing — critical slicing.
